### 2017-01-11 robust-software.tex

>>>>

Note: one practice \emph{not} included in the list below is the use of version control.
We think this is essential to building software of any kind
\cite{wilson2014,wilson2016}.
However,
our focus in this short guide is on the software that is built,
not on the process used to build it.
Similarly,
we do not explicitly discuss code review,
unit testing,
and other practices essential to maintainability and sustainable software development.
